### 2017-10-24 Draft2/Appendix.tex
Labels

\section{Proofs of Properties of Big-P Notation}

\subsection{Merging over Arithmetic Operations}
\label{MergingOverArithmetic}

@@

\begin{proof}
	We will consider the statement about addition first. Recall from the note at \ref{AsymptoticProperties} that this statement is equivalent to:

@@

\begin{proof}
	We will consider the statement about multiplication first. Recall from the note at \ref{AsymptoticProperties} that this statement is equivalent to:

@@

\subsection{Unique Class Lemma}
\label{UniqueClassOfFunctions}

\begin{lemma}
	Each function $f(n)$ has a unique class of functions under $P$. That is, suppose $f \in P(g(n))$ and $f \in P(h(n))$. Then $P(g(n)) = P(h(n))$.
\end{lemma}

\begin{proof}
	By definition, $\lim_{n \to \infty} \frac{f(n)}{g(n)} = 1$ and $\lim_{n \to \infty} \frac{f(n)}{h(n)} = 1$. Flipping the first equation and multiplying, we receive

	\begin{align*}
	\left( \lim_{n \to \infty} \frac {g(n)} {f(n)} \right) \left( \lim_{n \to \infty} \frac {f(n)} {h(n)} \right) &= 1\\
	\lim_{n \to \infty} \frac {g(n)} {h(n)} &= 1\\
	g &\in P(h(n))
	\end{align*}

	Now, consider any $\hat{g} \in P(g(n))$. Since

	\begin{align*}
	\lim_{n \to \infty} \frac {\hat{g}(n)} {g(n)} &= 1\\
	\left( \lim_{n \to \infty} \frac {\hat{g}(n)} {g(n)} \right) \left( \lim_{n \to \infty} \frac{g(n)}{h(n)} \right) &= 1\\
	\lim_{n \to \infty} \frac{\hat{g}(n)}{h(n)} &= 1
	\end{align*}

	it follows that $\hat{g} \in P(h(n))$, and thus $P(g(n)) \subseteq P(h(n))$. By a similar argument, it can be shown $P(h(n)) \subseteq P(g(n))$. Thus it must be true that $P(g(n)) = P(h(n))$.
\end{proof}

\subsection{Removal of Lower-Order Terms}
\label{RemovesLowerOrderTerms}

@@

	Then $f(n) + g(n) \in P(f(n))$. Since it is also true that $f(n) + g(n) \in P(f(n) + g(n))$, it follows from \ref{UniqueClassOfFunctions} that $P(f(n)) = P(f(n) + g(n))$.
\end{proof}

>>>>

\section{Proofs of $\TextTilde$ Properties}

\subsection{Merging over Arithmetic Operations}
\label{pf:MergingOverArithmetic}

@@

\begin{proof}
	We will consider the statement about addition first. Recall from the note at \ref{subsec:AsymptoticProperties} that this statement is equivalent to:

@@

\begin{proof}
	We will consider the statement about multiplication first. Recall from the note at \ref{subsec:AsymptoticProperties} that this statement is equivalent to:

@@

\subsection{Transitivity}
\label{pf:Transitivity}

\subsection{Removal of Lower-Order Terms}
\label{pf:RemovesLowerOrderTerms}

@@

	Then $f(n) + g(n) \in P(f(n))$. Since it is also true that $f(n) + g(n) \in P(f(n) + g(n))$, it follows from \ref{pf:Transitivity} that $P(f(n)) = P(f(n) + g(n))$.
\end{proof}

### 2017-10-24 Draft2/AsymptoticNotation.tex
Labels

\subsection{Properties}
\label{AsymptoticProperties}

A useful property $\TextTilde$ shares with $O$ is that it merges over arithmetic operations. This is stated by the following two theorems, which are proved in \ref{MergingOverArithmetic}.

@@

Another nice property $\TextTilde$ and $O$ have in common is that lower-order terms are removed from consideration. For example, $n \TextTilde n + \log_2 n$. This is stated by the below theorem, which is proved in \ref{RemovesLowerOrderTerms}.

>>>>

\subsection{Properties}
\label{subsec:AsymptoticProperties}

A useful property $\TextTilde$ shares with $O$ is that it merges over arithmetic operations. This is stated by the following two theorems, which are proved in \ref{pf:MergingOverArithmetic}.

@@

Another nice property $\TextTilde$ and $O$ have in common is that lower-order terms are removed from consideration. For example, $n \TextTilde n + \log_2 n$. This is stated by the below theorem, which is proved in \ref{pf:RemovesLowerOrderTerms}.
